---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nohrsc

<!-- badges: start -->
<!-- badges: end -->

The goal of nohrsc is to ...

## Minimum Viable Product
- Download data (use *apply to make >1 easy)
- Query/Load downloaded data
- Delete data

## First Improvement
- Force redownload (delete/overwrite existing data)
- Improve queries

## Second Improvement
- Allow clipping before storage to save disk space

## To Do

- [ ] Add tests  
- [ ] Use assertthat to check archive/raster filenames etc  

## Installation

You can install nohrsc using `remotes` by

``` r
remotes::install_github("jpshanno/nohrsc")
```

or without `remotes` by

``` r
nohrsc_source <- file.path(tempdir(), "nohrsc-master.zip")
download.file("https://github.com/jpshanno/nohrsc/archive/master.zip",
              nohrsc_source)
unzip(nohrsc_source,
        exdir = dirname(nohrsc_source))
install.packages(sub(".zip$", "", nohrsc_source),
                 repos = NULL,
                 type = "source")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(nohrsc)
## basic example code
```
